Constructing Sailing Match Race Schedules: Round-Robin Pairing Lists

### 2015-06-02 paper.tex
Don't cite as a noun
removed !

It was anticipated that this problem would be easy to model. This naivety was due to the use of the
term ``round-robin'' for these schedules, leading us to believe that we could use some of the models
already in the literature \cite{trick2002,trick2008,henz2004}. This naivety slowly dissolved as
we addressed more and more of the ISAF criteria. A number of models we produced were scrapped due to
misunderstanding about the actual problem, i.e.\ a communication problem between the authors.
Eventually this was resolved by presenting the majority of the criteria as a deterministic finite
automaton. This became our Rosetta Stone, with the surprising benefit that it not only improved the
teams communications, it was also a constraint!

@@

We have only reported a handful of our schedules, however there are missing schedules i.e.\ unpublished and not yet produced by us. Examples of
these are 10 skippers and 8 boats, 11 skippers with fewer than 10 boats, 12
skippers and 8 boats, 13 skippers and 8 boats and 14 skippers with fewer than 10 boats. None of these
schedules have been published by the ISAF, although we expect that they can be produced by
selectively violating some of constraints. We have also not yet encoded criterion~7, addressing the
situation of 10 or more boats. To do this we will have to modify the DFA constraint used in the
first two stages. In addition, we have yet to address the format of \emph{two-group} round-robin schedules as also found in \cite{isaf}.

>>>>

It was anticipated that this problem would be easy to model. This naivety was due to the use of the
term ``round-robin'' for these schedules, leading us to believe that we could use some of the models
already in the literature \cite{trick2002,trick2008,henz2004}. This naivety slowly dissolved as
we addressed more and more of the ISAF criteria. A number of models we produced were scrapped due to
misunderstanding about the actual problem, i.e.\ a communication problem between the authors.
Eventually this was resolved by presenting the majority of the criteria as a deterministic finite
automaton. This became our Rosetta Stone, with the surprising benefit that it not only improved the
teams communications, it was also a constraint.

@@

We have only reported a handful of our schedules, however there are missing schedules i.e.\ unpublished and not yet produced by us. Examples of
these are 10 skippers and 8 boats, 11 skippers with fewer than 10 boats, 12
skippers and 8 boats, 13 skippers and 8 boats and 14 skippers with fewer than 10 boats. None of these
schedules have been published by the ISAF, although we expect that they can be produced by
selectively violating some of constraints. We have also not yet encoded criterion~7, addressing the
situation of 10 or more boats. To do this we will have to modify the DFA constraint used in the
first two stages. In addition, we have yet to address the format of
\emph{two-group} round-robin schedules as also found in the manual \cite{isaf}.
